The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-06-27 head.tex
修改摘要

In this paper,
(study the resource servitization in the transitions way)
(propose a operation model for user to describe the transitions in the system) 
(in the god view as evolution to see the service pattern in a statistic view)
(simulate all this in an agent-bade method)
(evaluate which service pattern is effective for the resource user and environment friendly)
(make a proper explanation of all the emergency of the evolution)

>>>>

In this paper, we proposed an operation model for users to support their transitions in the manufacturing ecosystem, and we also proposed an adjustment method to guide these transitions to make a manufacturing service pattern evolution. 
With the help of Repast Simphony, we designed an agent-based model to simulate the ecosystem. As the simulation output, the emergence resource servitization and optimization pattern implies the effectiveness and validity of the proposed operation model and adjustment method that can be adopted in the real Cloud Manufacturing world.
